Articles of Association of London Hackspace Ltd.

### 2011-07-20 constitution/articles-body.tex
Specify a maximum number of directors.
Alter quorum for general meetings. 1/10th of membership is actually quite large.

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is:
    \begin{enumerate}
    \item 10 members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting; or
    \item
      one tenth of the total membership at the time
    \end{enumerate}
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

@@

\item
  \begin{enumerate}
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three but (unless
  otherwise determined by ordinary resolution) shall not be subject
  to any maximum.

>>>>

\item
  \begin{enumerate}
  \item
    No business shall be transacted at any general meeting unless a
    quorum is present.
  \item
    A quorum is 10 members present in person or by proxy and entitled to vote upon
      the business to be conducted at the meeting.
  \item
    The authorised representative of a member organisation shall be
    counted in the quorum.
  \end{enumerate}

@@

\item
  \begin{enumerate}
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three, nor more than eight.
